The transboundary nature of the world’s exploited marine species

### 2021-03-14 Scripts/Manuscript_Draft.Rmd
fixed crash

---
output:
  bookdown::word_document2
  # bookdown::pdf_book:
#     toc : no
#     keep_tex: no
#     number_sections: yes
#     fig_width: 6 
#     fig_height: 4 
# geometry: margin=1in
bibliography: ../References/FishForVisa_Ref.bib
csl: ../References/nature_cc.csl
---

@@

```{r supplements, child = 'supplements.Rmd', eval = F}
```

>>>>

---
output:
  # bookdown::word_document2
  bookdown::pdf_book:
    toc: no
    keep_tex: no
    number_sections: yes
    fig_width: 6
    fig_height: 4
# geometry: margin=1in
# bibliography: ../References/FishForVisa_Ref.bib
# csl: ../References/nature_cc.csl
---

@@

```{r supplements, child = 'supplements.Rmd', eval = T}
```
